---
title: "02 Data Acqusition"
date: "2022-05-10"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Bored? Let's find you something

## Loading Libraries
```{r}
library(httr)
library(tidyverse)
```

## Getting Data
```{r}
get_data <- function() {
  url <- "http://www.boredapi.com/api/activity/"
  GET(url) %>% content(as="parsed")
}

num_iter = c(1:10)
for (i in num_iter){
  if (i==1){
    data_from_web <- as_tibble(get_data())
  } 
  else{
    data_from_web <-  get_data() %>% 
      as_tibble() %>% 
      bind_rows(data_from_web)
  }
}
```
## Post processing the data

```{r}
data_from_web <- data_from_web %>%  
  mutate_all( na_if, "") %>% 
  select(-key)
```

## There you go. Have Fun!
```{r}
data_from_web
```
*Don't like the activities? re-run the file and find yourself new possibilities.*


### Description of columns:

* **type**: Type of the activity ["education", "recreational", "social", "diy", "charity", "cooking", "relaxation", "music", "busywork"]


* **participants**: The number of people that this activity could involve [0, n]


* **price**: A factor describing the cost of the event with zero being free [0, 1]

* **accessibility**: A factor describing how possible an event is to do with zero being the most accessible [0.0, 1.0]


# Scraping competitor website

## Loading Libraries
```{r}
library(rvest)
library(glue)
```
## Base URL and Helper function
```{r}
base_url <- "https://www.rosebikes.com"
read_paths <- function(path, css_selector){
  base_url %>% 
  glue(path) %>%
  read_html() %>% 
  html_nodes(css = css_selector) %>%
  html_attr("href")
}
```
## Getting Catalogs
```{r}
catalogs <- read_paths(path="/bikes", css_selector = ".catalog-navigation__link")[1:7]
```

## Getting Categories
```{r}
categories <- map(catalogs, read_paths, css_selector =".catalog-navigation__link" )
categories[[1]] <- categories[[1]][2:5]
categories[[2]] <- categories[[2]][2:3]
categories[3:7] <- catalogs[3:7]
```

## Getting Models
```{r}
models <- list()
for (category in categories){
  temp = map(category, read_paths, css_selector=".catalog-category-bikes__button")  
  models <- append(models, temp)
}
```

## Getting Model types
```{r}
get_model_types <-function(model_type){
  base_url %>% 
    glue(model_type) %>% 
    read_html() %>% 
    html_nodes("h3.basic-headline__title") %>% 
    html_text()
}

model_types <- list()
for (model in models){
  temp = map(model, get_model_types)  
  model_types <- append(model_types, temp)
}
model_types[[4]] = model_types[[4]][5:10] 
model_types[[11]] = model_types[[11]][3:20]
```
## Getting Prices
```{r}
replace_values =c(" "="", "\n"="", "€"="", ","="")

get_prices <-function(model_type){
  base_url %>% 
    glue(model_type) %>% 
    read_html() %>% 
    html_nodes(css=".product-tile-price__current-value") %>%
    html_text() %>% 
    str_replace_all(replace_values) %>% 
    as.numeric()
}

prices <- list()
for (model in models){
  temp = map(model, get_prices)
  prices <- append(prices, temp)
}

```
## Assembling Everything in single table
```{r message=FALSE, warning=FALSE}
models_tbl <- tibble() 
model_types_tbl <- tibble()
prices_tbl <- tibble()
counter = 1
for (model in models){
  for (sp_model in model){
  models_tbl <- bind_rows(models_tbl, 
                          matrix(sp_model %>% 
                                   rep(times= length(prices[[counter]]))) %>% 
                            set_names(c("a")))
  model_types_tbl <- bind_rows(model_types_tbl, 
                               matrix(model_types[[counter]]) %>% 
                                 set_names(c("b")))
  prices_tbl <- bind_rows(prices_tbl,
                          matrix(prices[[counter]]) %>% 
                            set_names(c("c")))
  counter = counter +1
  if (counter==19){
    break
  }
  }
  if (counter==19){
    break
  }
}
final_data_tbl <- models_tbl %>% 
  bind_cols(model_types_tbl) %>%
  bind_cols(prices_tbl) %>% 
  separate(col= "...1", into = c("empty", "vehicle","Sub_category_1", "Sub_category_2", "Sub_category_3"), sep = "/" ,remove = FALSE) %>% 
  rename("URL"="...1", "Model"="...2", Price="...3") %>% 
  select(-2,-3)
  

```
## Results

```{r message=FALSE, warning=FALSE}
final_data_tbl %>% head(n=10)
```

